\bf Title here

### 2020-07-06 paper/paper.Rmd
define projection and index function

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their intial paper on projection pursuit in 1974 that "the  technique  use  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied to more general to help practitioner to unveil the black-box in randomised iteartive (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

From Section \ref{tour}, we presents a comprehensive case study on how to use the visual diagnostics to explore the optimisation in a specific problem: projection pursuit guided tour. Section \ref{tour} aims to provide non-experts with an overview of the problem content and the existing optimisation procedures used in projection pursuit guided tour. For those who are already familiar with the technique, this section can be skipped.

The optimisation problem we're interested in is in the context of projection pursuit. Coined by @friedman1974projection, projection pursuit is a method that detects the interesting structure (i.e. clustering, outliers and skewness) of multivariate data via projecting it in lower dimensions. A Projection Pursuit Index (PPI) is a function of the projection matrix (a.k.a projection angle, projection basis) measuring the "interestingness" of data and we refer the value of PPI function as *index value*. In the literature, the indices being proposed include Legendre index [@friedman1974projection], hermite index [@hall1989polynomial], natural hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection]. [Any literature on holes index? xxx]

>>>>

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their intial paper on projection pursuit in 1974 that "the  technique  use  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied to more general to help practitioner to unveil the black-box in randomised iteartive (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
preamble: >
  \usepackage{amssymb}
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

From Section \ref{tour}, we presents a comprehensive case study on how to use the visual diagnostics to explore the optimisation in a specific problem: projection pursuit guided tour. Section \ref{tour} aims to provide non-experts with an overview of the problem content and the existing optimisation procedures used in projection pursuit guided tour. For those who are already familiar with the techniques, feel free to skip this section.

The optimisation problem we're interested in is in the context of projection pursuit. Coined by @friedman1974projection, projection pursuit is a method that detects the interesting structure (i.e. clustering, outliers and skewness) of multivariate data via projecting it in lower dimensions. Let $D_{n \times p}$ be a data matrix, an n-d projection can be seen as a linear transformation: $T: \mathbb{R}^p \mapsto \mathbb{R}^d$ defined by $P = D \cdot A$, where $A_{p\times d}$ is the projection basis and $P_{n \times p}$ is the projected data. Define $f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}$ be an index function that maps the projection basis $A$ onto a scalar value $I$, this function is commonly known as the projection pursuit index (PPI) function, or indice function,  that can be used to measure the "interestingness" of the projection. A number of indice functions have been proposed in the literature and this includes Legendre index [@friedman1974projection], hermite index [@hall1989polynomial], natural hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection]. [Any literature on holes index? xxx]

### 2020-07-06 paper/paper.tex
define projection and index function

%% load any required packages here

@@

From Section \ref{tour}, we presents a comprehensive case study on how
to use the visual diagnostics to explore the optimisation in a specific
problem: projection pursuit guided tour. Section \ref{tour} aims to
provide non-experts with an overview of the problem content and the
existing optimisation procedures used in projection pursuit guided tour.
For those who are already familiar with the technique, this section can
be skipped.

The optimisation problem we're interested in is in the context of
projection pursuit. Coined by \citet{friedman1974projection}, projection
pursuit is a method that detects the interesting structure
(i.e.~clustering, outliers and skewness) of multivariate data via
projecting it in lower dimensions. A Projection Pursuit Index (PPI) is a
function of the projection matrix (a.k.a projection angle, projection
basis) measuring the ``interestingness'' of data and we refer the value
of PPI function as \emph{index value}. In the literature, the indices
being proposed include Legendre index \citep{friedman1974projection},
hermite index \citep{hall1989polynomial}, natural hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}. {[}Any literature on holes index?
xxx{]}

>>>>

%% load any required packages here
\usepackage{amssymb}

@@

From Section \ref{tour}, we presents a comprehensive case study on how
to use the visual diagnostics to explore the optimisation in a specific
problem: projection pursuit guided tour. Section \ref{tour} aims to
provide non-experts with an overview of the problem content and the
existing optimisation procedures used in projection pursuit guided tour.
For those who are already familiar with the techniques, feel free to
skip this section.

The optimisation problem we're interested in is in the context of
projection pursuit. Coined by \citet{friedman1974projection}, projection
pursuit is a method that detects the interesting structure
(i.e.~clustering, outliers and skewness) of multivariate data via
projecting it in lower dimensions. Let \(D_{n \times p}\) be a data
matrix, an n-d projection can be seen as a linear transformation:
\(T: \mathbb{R}^p \mapsto \mathbb{R}^d\) defined by \(P = D \cdot A\),
where \(A_{p\times d}\) is the projection basis and \(P_{n \times p}\)
is the projected data. Define
\(f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}\) be an index function
that maps the projection basis \(A\) onto a scalar value \(I\), this
function is commonly known as the projection pursuit index (PPI)
function, or indice function, that can be used to measure the
``interestingness'' of the projection. A number of indice functions have
been proposed in the literature and this includes Legendre index
\citep{friedman1974projection}, hermite index
\citep{hall1989polynomial}, natural hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}. {[}Any literature on holes index?
xxx{]}
